What is happening on Twitter? A framework for student research projects with tweets

### 2020-08-22 Rmd/jse-special-issue-2020-october.Rmd
created a new Rmd for revised text

---
title: "What is happening on Twitter? A framework for student research projects with tweets"
author: ""
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

Studies of Twitter conversations have yielded valuable insights into 
modern culture. Using large collections of tweets, scholars have 
investigated diverse research questions, including
the inference of relationships and social networks among Twitter users [@lin2011joint]; 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
rhetoric in recruiting political supporters.
Recognizing the potential utility of tweets for data science research and teaching, 
we created a collection of tweets over time by repeated querying of the Twitter streaming API.

@@

We thank the special issue 
editors and anonymous reviewers for their constructive comments and suggestions.

@@

1. Data dictionary

@@

1. tweets.Rmd
1. tweets-one.Rmd
1. recover\_tweets.R

@@

1. Student 1 poster
1. Student 1 report
1. Student 2 useR 2016 slides
1. Student 2 poster

@@

1.

>>>>

---
title: "What is happening on Twitter? A framework for student research projects with tweets"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

Studies of Twitter conversations have yielded valuable insights into 
modern culture. Using large collections of tweets, scholars have 
investigated diverse research questions, including
the inference of relationships and social networks among Twitter users [@lin2011joint]; 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
rhetoric in recruiting political supporters [@pelled2018little;@wells2016trump].
Recognizing the potential utility of tweets for data science research and teaching, 
we created a collection of tweets over time by repeated querying of the Twitter streaming API.

@@

The authors thank Betsy Colby Davie and Rick Nordheim for helpful discussions and 
feedback on preliminary versions of the manuscript. We thank the special issue 
editors and anonymous reviewers for their constructive comments and suggestions.

@@

1. [Data dictionary](https://github.com/fboehm/jse-2019/blob/master/data/tweets-data-dictionary.csv)

@@

1. [tweets.Rmd](https://raw.githubusercontent.com/fboehm/jse-2019/master/Rmd/tweets.Rmd)
1. [tweets-one.Rmd](https://raw.githubusercontent.com/fboehm/jse-2019/master/Rmd/tweets-one.Rmd)
1. [recover\_tweets.R](https://raw.githubusercontent.com/fboehm/jse-2019/master/Rmd/recover_tweets.R)

@@

1. Student 1 poster: [Project\_Poster.pdf](https://github.com/fboehm/jse-2019/blob/master/supplementary/Project_Poster.pdf)
1. Student 1 report: [report.pdf](https://github.com/fboehm/jse-2019/blob/master/supplementary/report.pdf)
1. Student 2 useR 2016 slides: [user2016boehm.pdf](https://github.com/fboehm/jse-2019/blob/master/supplementary/user2016boehm.pdf) 
1. Student 2 poster: [warfdiscovery2016boehm.tiff](https://github.com/fboehm/jse-2019/blob/master/supplementary/warfdiscovery2016boehm.tiff)

@@

1. https://github.com/fboehm/jse-2019
